\begin{thebibliography}{99}
	
	\addcontentsline{toc}{chapter}{\large{Bibliographie}}
	
	\bibitem{Bi} Bishop W., Petro J.W., Ratliff Jr L. J. et Rush D.,\textit{ Note on noetherian filtrations}, Communications in Algebra, Vol.17, No. 2, 1988, pp. 471-485.
	
	\bibitem{Di1} Dichi H.,\textit{ Integral dependence over a filtration}, Journal of Pure and Applied Algebra, Vol. 58, No. 1, 1989, pp. 7-18. 
	
	\bibitem{Di2} Dichi H., \textit{Travaux de recherches, en vue de l'habilitation à diriger une recherche}, 1999.
	
	\bibitem{Di3} Dichi H., Sangare D., et Soumare M.,\textit{ Filtrations, integral dependence, reduction, f-good filtrations}, Communications in Algebra, Vol. 20, No. 8, 1992, pp. 2393-2418.
	
	\bibitem{Di4} Dichi H. et Sangaré D.,\textit{ Filtrations, asymptotic ans prüferian closures, cancellation laws}, Proceedings of the American Mathematical Society, Vol. 113, No. 3, 1991, pp. 617-624. 
	
	\bibitem{Eak} Eakin P., \textit{The converse to a well known theorem on noetherian rings}, Math. Ann., Vol. 177, 1968, pp. 278-282.
	
	\bibitem{No} Northcott D. G., et Rees D.,\textit{ Reductions of ideals in local rings}, in Mathematical Proceedings of the Cambridge Philosophical Society, Vol. 50, No. 2, 1954, pp. 145-158.
	
	\bibitem{Ok} Okon J. S., et Ratliff L,\textit{ Reductions of filtrations}, Pacific Journal of Mathematics, Vol. 144, No. 1, 1990, pp. 137-154.
	
	\bibitem{Ra1} Ratliff Jr L. J.,\textit{ Notes on essentially powers filtrations}, Michigan Mathematical Journal, Vol.26, No. 3, 1979, pp. 313-324.
	
	\bibitem{Ra2} Ratliff Jr L. J. et Rush D.,\textit{ Note on I-good filtrations and noetherian Rees rings}, Communications in Algebra, Vol.16, No. 5, 1988, pp. 955-975.

\end{thebibliography}
